---
title: Using co-occurence networks to map soilscapes
author:
  - name: Dylan Beaudette
    email: debeaudette@ucdavis.edu
    affiliation: NRCS
  - name: Pierre Roudier
    email: roudierp@landcareresearch.co.nz
    affiliation: MW,TPM
    footnote: Corresponding Author
  - name: Dion O'Neale
    affiliation: TPM
address:
  - code: NRCS
    address: USDA -- NRCS, Sonora, CA, USA
  - code: MW
    address: Manaaki Whenua -- Landcare Research, Palmerston North, New Zealand
  - code: TPM
    address: Te Pūnaha Matatini, A New Zealand Centre of Research Excellence, Private Bag 92019, Auckland 1142, New Zealand

abstract: |
  Soils are arguably one of the most complex materials on Earth, and present a unique challenge for those seeking to constrain spatial variability within the context of soil survey. Across the landscape, different soil types will often be spatially intermingled. This is reflected by soil mapping units that are often composed of more than one soil taxa. The research field of network science offers new mathematical tools to visualize and analyze existing soil survey data, and explore its complex relational interactions. In this paper, we extract and visualize pedological information by analyzing the co-occurrence of soil taxa using a network approach. For any level of a given hierarchical soil classification system, the co-occurrence of soil taxa within and between neighboring soil mapping units can be described as a network graph. The structural properties of the resulting graphs can be analyzed, and tools such as community structure detection are used to classify their different nodes. Soilscapes are then delineated by mapping the identified communities back in geographical space. This approach also gives a method for quantifying the pedological complexity of different regions based on their constituent soil types, using metrics such as graph connectivity. Different levels of granularity for both the regional data and the soil classification data allow for views at different scales. Network science offers the opportunity of new insights from looking at existing data in a new way. Soil survey data from USDA-NRCS (USA) is used to illustrate the value and originality of these new approaches. 
  
  In this study, we analysed the soil map produced by conventional mapping using tools from the field of network science [REFERENCE]. Namely, these tools were used to analyse the co-occurence of different soil series over the survey area.

  
preamble: 
  \usepackage{subcaption}
  
bibliography: references.bib
output:
  base_format: rticles::elsevier_article
  citation_package: natbib
  fig_caption: yes
  
---

Introduction
============

Soil survey traditionally represents soils in the landscapes as a set of polygons, thate are populated with one or more soil concepts. 

Despite the rise of predictive techniques as a way to produce new soil information, a considerable amount of knowledge resides in legacy soil surveys. 

- 1977, 1985: F.D. Hole, soilscapes defines patterns of association
- 2001: P. Lagacherie et al., soilscapes as landscape signature
- 2010: A.E. Hewitt et al., soilscapes as modeling domains 
- 2013/2016: J.D. Phillips, spatial adjacency of mapping units
- 2013--current: SoilWeb Series Data Explorer
- Review paper -- Graph theory in the geosciences http://app.mtu.edu.ng/cbas/Geoscience/Graph%20theory%20in%20the%20geosciences.pdf

Application of networks in soil science/geomorphology: @heckmann2015graph, @phillips2015graph, @phillips2016identifying

This paper focusing in quantifying and mapping co-occurrence from tabular data (ie excluding spatial adjacency). To make the introduction of those new methods easier, it is ignoring the spatial adjacency. 


Define:
- soil series
- map unit
- soil series / component relationship
- sibling
- component kind / percentage
- components inherit from the soil series, but more specific, not all instances the "same"
- components ommited in this approach (higher taxa, misc. area)
- soil survey area and vintage
- soilscape / catena / soil-landscape model
- connections between NCSS map unit (suites of MU really) and the soilscape / catena
- vertex, edge, edge weight
- community matrix
- components | series (rows) x map units (columns) --> component percentages (cells)
- pick a consistent term: "cluster" or "soilscape `n`"


Key Points
- soil series are convenient containers / labels for soil property / condition (depth) functions + covariance structure
- components inherits from soil series as repeating


Graph
- community detection: pros / cons (I'm not very familiar with underlying algorithm, e.g. how is `n` set?)
- linkages between communities: significance of those components that connect between communities
- island communities: usually represent contrasting properties or conditions that affect management (see clusters 6, 12)


Methods / Data Prep
- filtering of components: some MU / components not present in the final graph (quantify area / number)
- adjacency built from component names, higher-taxa not specific enough | name collisions | overly-complex (noisy) graph




Material and Methods
====================

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  dev = "png",
  dpi = 200,
  echo=FALSE, 
  message=FALSE, 
  warning=FALSE
  )
options(scipen = 999)
```

```{r libs, echo=FALSE, message=FALSE}
# Utils
library(dplyr)

# Spatial 
library(sf)
library(rgdal)
library(sp)

# Graphs
library(igraph)
library(networkD3)

# Soil
library(sharpshootR)

# Datavis
library(RColorBrewer)
library(ggplot2)
library(ggsn)
library(ggraph)
library(ggmap)
library(ggforce)
library(hrbrthemes)
library(patchwork)
# library(cowplot)
```

```{r data, echo=FALSE}
# load cached data

#load('../data/cached-nasis.rda')
# load('../data/cached-mu.rda')
# load('../data/cached-graph.rda')

x <- readRDS('../data/component-data.rda')
mu <- readRDS('../data/spatial-data.rda')
g <- readRDS('../data/graph.rda')
d <- readRDS('../data/vertices_df.rda')
leg <- readRDS('../data/legend.rda')
```

```{r preprocessing, echo=FALSE, cache=TRUE}
# ## associate nodes with map units, two options:
# ## simple majority:
# ## membership by component percent:
# 
# # simple method: reduce mukey--compname to 1:1 via majority rule
# # assumption: there are never >1 components with the same name
# # caveat: some map unit symbols will have NO association with graph, based on previous subsetting rules: NULL delineations on map
# mu.agg.majority <- function(i) {
#   # keep the largest component
#   idx <- order(i$comppct_r, decreasing = TRUE)
#   res <- i[idx, ][1, , drop=FALSE]
#   return(res)
# }
# 
# # create mu -> graph lookup table
# # mu.LUT <- plyr::ddply(x, 'musym', mu.agg.majority)
# mu.LUT <- plyr::ddply(x, 'mukey', mu.agg.majority)
# 
# # compnames in graph but not mu.LUT
# # setdiff(V(g)$name, unique(mu.LUT$compname))
# # 
# # in mu.LUT but not in graph
# # setdiff(unique(mu.LUT$compname), V(g)$name)
# 
# # join mukey -- graph via component name
# d <- plyr::join(mu.LUT, d, by='compname')
# 
# # join() / merge() do strange things in the presence of NA...
# d.no.na <- d[which(!is.na(d$mukey)), ]
# 
# # samity-check: mukey in map missing from graph--mukey association
# # none missing: good
# if ( length(setdiff(unique(x$mukey), d.no.na$mukey)) > 0 ) stop()
# 
# # sanity check: there should be a 1:1 relationship between
# # OK
# if (! (all(rowSums(as.matrix(table(d$mukey, d$cluster))) < 2)) ) stop()
# 
# ## note: there are a couple clusters without corresponding polygons!
# # this breaks in the presence of NA...
# mu <- merge(mu, d.no.na, by.x='mukey', by.y='mukey')
# 
# # filter-out polygons with no assigned cluster
# mu <- mu[which(!is.na(mu$cluster)), ]
# 
# # TODO: investigate map units (mukey) that aren't represented in the graph
# # x[which(x$mukey %in% unique(mu[which(is.na(mu$cluster)), ]$mukey)), ]
# 
# # aggregate geometry based on cluster labels
# mu.simple <- rgeos::gUnionCascaded(mu, as.character(mu$cluster))
# mu.simple.spdf <- sp::SpatialPolygonsDataFrame(mu.simple, data=data.frame(ID=sapply(slot(mu.simple, 'polygons'), slot, 'ID')), match.ID = FALSE)

mu_sf <- st_read('../data/graph-and-mu-polygons.shp', quiet = TRUE)
# saveRDS(mu, '../outputs/mu_ca.rda')
```

```{r expert_interpretation, echo=FALSE, cache=TRUE, message=FALSE}

expert <- readr::read_csv('../expert-interp.csv') %>%
  dplyr::mutate(cluster = as.character(cluster))

## DEB: this is already done in ../generate-network.R

# # Upload expert notes to graph nodes
# V(g)$notes <- expert$notes[V(g)$cluster]

## DEB: the combination of notes into cluster narrative is done in ../generate-network.R
## TODO: save this cluster narrative when creating ../data/graph-and-mu-polygons.shp

# Upload expert notes to polygons
mu_sf <- mu_sf %>%
  dplyr::mutate(cluster = as.character(cluster)) %>%
  dplyr::left_join(expert, by = "cluster")

# # # Union based on cluster ID
# # mu_union <- mu_sf %>%
# #   dplyr::mutate(cl = as.character(cluster)) %>% 
# #   dplyr::group_by(cl) %>% 
# #   dplyr::summarise(color = unique(color), notes = unique(notes))
# 
# # saveRDS(mu_union, '../outputs/mu_union_ca.rda')
```

```{r abundance, cache=TRUE}
# abundance <- dplyr::left_join(select(mu_sf, muiid), x) %>% 
abundance <- mu %>% #dplyr::left_join(select(mu_sf, gid, mukey), x) %>%
  st_as_sf() %>% 
  dplyr::select(gid, mukey) %>% 
  dplyr::left_join(x) %>% 
  dplyr::mutate(
    area = sf::st_area(.),
    area_w = area * comppct_r / 100 # Weigthed area
  ) %>% 
  st_set_geometry(NULL) %>%
  dplyr::mutate(area_dbl = as.numeric(area_w)) %>% 
  dplyr::group_by(compname) %>% 
  dplyr::summarise(area = sum(area_dbl)) %>% 
  dplyr::mutate(abundance_ha = units::set_units(measurements::conv_unit(area, from = "m2", "hectare"), "ha")) #%>% 
  # dplyr::summarise(tot_area_ha = sum(abundance_ha))
```

## Study site

```{r map_context, echo=FALSE, cache=TRUE}
roi <- mu %>% 
  st_as_sf %>% 
  st_union %>% 
  st_buffer(dist = 5000) %>% 
  st_buffer(dist = -5000)

state <- ggplot2::map_data('state')

roi_wgs <- roi %>% 
  st_transform(crs = 4326) %>% 
  as("Spatial") %>% 
  fortify

# us_states <- st_transform(sf::st_as_sf(maps::map('state', plot = FALSE, fill = TRUE)), crs = 102003)
us_states <- st_transform(sf::st_as_sf(maps::map('state', plot = FALSE, fill = TRUE)), crs = 2163)
  
m_context <- ggplot() + 
  geom_sf(data = us_states, fill = "grey80") + 
  geom_sf(data = dplyr::filter(st_transform(sf::st_as_sf(maps::map('state', plot = FALSE, fill = TRUE)), crs = 2163), ID == "california"), fill = "grey50") +
  geom_sf(data = roi, fill = "red") +
  ggsn::north(data = us_states, location = "bottomright") +
  ggsn::scalebar(data = us_states, transform = FALSE, dist = 500, dist_unit = "km", location = "bottomleft", st.size = 3) +
  labs(x = "", y = "") +
  theme_bw()

m_context_zoom <- ggplot() + 
  geom_sf(data = dplyr::filter(us_states, ID == "california"), fill = "grey50") +
  geom_sf(data = roi, fill = "red") +
  ggsn::north(data = dplyr::filter(us_states, ID == "california")) +
  ggsn::scalebar(data = dplyr::filter(us_states, ID == "california"), transform = FALSE, dist = 200, dist_unit = "km", location = "bottomleft", st.size = 3) +
  labs(x = "", y = "") +
  theme_bw()

# m_context <- ggplot() + 
#   geom_polygon(data = state, aes(x = long, y = lat, group = group), fill = "grey80", size = 0.2, colour = "grey90") +
#   geom_polygon(data = dplyr::filter(state, region == "california"), aes(x = long, y = lat, group = group), fill = "grey70", colour = "grey90") +
#   geom_polygon(data = roi_wgs, aes(x = long, y = lat, group = group), fill = "red") + 
#   ggforce::facet_zoom(xy = region == "california", zoom.size = 0.8) + 
#   coord_map("albers", lat0 = 39, lat1 = 45) + 
#   theme_bw() + 
#   labs(x = "", y = "")

#print(m_context + m_context_zoom)
```

This study focused on a `r prettyNum(units::drop_units(round(measurements::conv_unit(sf::st_area(roi), "m2", "hectare"))), big.mark = ",")` ha area located in the foothills of the Sierra Nevada in California, USA (Figure \ref{fig:map_survey}). 
The mean annual rainfall/altitude/etc... 

## Conventional soil survey

The soils of the study site were surveyed conventionally by the NRCS...

The result of this survey is a map of `r prettyNum(nrow(mu), big.mark = ",")` polygons over the region (Figure \ref{fig:map_survey}).

Probably explain the concept of MU here too.

```{r map_survey, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="\\label{fig:map_survey}Context of the study, showing the outlines of the mapping units present in the soil survey. The study site is located on the foothills of the Sierra Nevada in California, USA.", cache=TRUE}
m_survey <- ggplot(st_as_sf(mu)) +
  geom_sf(lwd = 0.1) +
  ggsn::north(data = st_as_sf(mu)) +
  ggsn::scalebar(data = st_as_sf(mu)[, 'geometry'], transform = FALSE, dist = 10, dist_unit = "km", location = "bottomleft", st.size = 3) +
  labs(x = "", y = "") +
  theme_bw()

(m_context / m_context_zoom) | m_survey
```

\begin{table}
\centering
\begin{tabular}{ccc}
\hline
mu & component & pct \\
\hline
1612048 & Amador & 45 \\
1612048 & Gillender & 40 \\
1612048 & Ranchoseco & 6 \\
1612048 & Vleck & 3 \\
1612048 & Pardee & 3 \\
1612048 & Peters & 3 \\
... & ... & ... \\
2766838 & Amador & 76 \\
2766838 & Gillender & 9 \\
2766838 & Pardee & 5 \\
2766838 & Miltonhills & 5 \\
2766838 & Redding & 3 \\
\hline
\end{tabular}
\caption{Example of tabular soil survey data. mu: map unit code. component: name of the soil serie identified in the map unit. pct: relative percentage of the soil serie within that map unit, as estimated by the pedologist. Source: XXXX.}
\label{tab:sim_mat_1}
\end{table}


## Representing soil series co-occurence

<!-- The results of the soil survey were analysed using tools from the network science field.  -->
<!-- All data analysis was done in R [REFERENCE]. -->

### Soil siblings

The conventional soil survey data was organised in a tabular fashion, based on map units. 
One or more soil series were associated within each map unit delineated over the survey area. 
Additionally, the relative proportion of each soil series within each map unit was estimated by the pedologist who surveyed the area (Table \ref{tab:sim_mat_1}). 
In this study, we focus on the co-occurrence of different soil series within the polygonal map units. 
We propose that the soil series that co-occur in at least one map unit are referred to as being "soil siblings". 
An example of this concept is presented on a subset of the soil survey data, in Table \ref{tab:sim_mat_1}. 
In this example, the soil series \textit{Amador}, \textit{Gillender}, \textit{Ranchoseco}, \textit{Vleck}, \textit{Pardee}, and \textit{Peters} are all siblings, because they are all co-occurring in map unit "1612048". 
However, \textit{Vleck} and \textit{Miltonhills} are \emph{not} siblings (at least on that specific subset of the soil survey data) since they do not co-occur in either of the two map units presented. 
It is important to note that there is not necessarily any taxonomical links between siblings: the only condition for two soil series to be "siblings" is that they need to be mapped within same map units at least once. 

### Quantifying soil series associations

An intuitive way to detect soil siblings, and therefore represent the co-occurrence between the different soil series present in the surveyed region, is to compute a co-occurrence matrix [@legendre2012numerical]. 
A co-occurrence matrix tabulates the number of times each possible combination of two soil series co-occur in map units of the surveyed area (Table \ref{tab:sim_mat_2}). 

<!-- \begin{table}[!htb] -->
<!--     \caption{Global caption} -->
<!--     \begin{subtable}{.5\linewidth} -->
<!--       \centering -->
<!--         \caption{Co-occurence matrix derived from the subset of soil suvey data presented in Table \ref{tab:sim_mat_1}.} -->
<!--         \begin{tabular}{cccccccc} -->
<!--           \hline -->
<!--            & Gillender & Miltonhills & Pardee & Peters & Ranchoseco & Redding & Vleck \\ -->
<!--           \hline -->
<!--           Amador & 2 & 1 & 2 & 1 & 1 & 1 & 1 \\ -->
<!--           Gillender & 0 & 1 & 2 & 1 & 1 & 1 & 1\\ -->
<!--           Miltonhills & 0 & 0 & 1 & 0 & 0 & 1 & 0\\ -->
<!--           Pardee & 0 & 0 & 0 & 1 & 1 & 1 & 1 \\ -->
<!--           Peters & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\ -->
<!--           Ranchoseco & 0 & 0 & 0 & 0 & 0 & 0 & 1 \\ -->
<!--           Redding & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Vleck & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\  -->
<!--           \hline -->
<!--         \end{tabular} -->
<!--     \end{subtable}% -->
<!--     \vfill -->
<!--     \begin{subtable}{.5\linewidth} -->
<!--       \centering -->
<!--         \caption{Pseudo-community matrix derived from the soil survey data. Each row represents a soil series, while each column represent a map unit code. The tranformation used the relative percentage of soil siblings to weight the presence of soil siblings across the different map units.} -->
<!--         \begin{tabular}{ccccccccc} -->
<!--           \hline -->
<!--            & 461845 & 461980 & 462528 & 462529 & 462530 & 462531 & 462954 & 462955 \\ -->
<!--           \hline -->
<!--           Amador & 45 & 25 & 85 & 85 & 85 & 85 & 85 & 85 \\ -->
<!--           Corning & 0 & 5 & 0 & 0 & 0 & 0 & 0 & 0\\ -->
<!--           Exchequer & 0 & 0 & 5 & 5 & 5 & 5 & 0 & 0\\ -->
<!--           Gillender & 40 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Hornitos & 0 & 0 & 5 & 5 & 5 & 5 & 10 & 10 \\ -->
<!--           Inks & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Miltonhills & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Pardee & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Pentz & 0 & 0 & 5 & 5 & 5 & 5 & 5 & 5 \\ -->
<!--           Peters & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Ranchoseco & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Redding & 0 & 4 & 0 & 0 & 0 & 0 & 0 & 0 \\ -->
<!--           Vleck & 3 & 40 & 0 & 0 & 0 & 0 & 0 & 0\\ -->
<!--           \hline -->
<!--           \end{tabular} -->
<!--     \end{subtable}  -->
<!-- \end{table} -->


\begin{table}
\centering
\begin{tabular}{cccccccc}
\hline
 & Gillender & Miltonhills & Pardee & Peters & Ranchoseco & Redding & Vleck \\
\hline
Amador & 2 & 1 & 2 & 1 & 1 & 1 & 1 \\
Gillender & 0 & 1 & 2 & 1 & 1 & 1 & 1\\
Miltonhills & 0 & 0 & 1 & 0 & 0 & 1 & 0\\
Pardee & 0 & 0 & 0 & 1 & 1 & 1 & 1 \\
Peters & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
Ranchoseco & 0 & 0 & 0 & 0 & 0 & 0 & 1 \\
Redding & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Vleck & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\ 
\hline
\end{tabular}
\caption{Co-occurence matrix derived from the subset of soil suvey data presented in Table \ref{tab:sim_mat_1}}
\label{tab:sim_mat_2}
\end{table}

Unfortunately, using this method, the information about the relative likelihood to find a soil series in a given map unit  (typically represented by the pedologist for each map unit as a relative percentage for each soil sibling) is lost in the process. 
A workaround this issue is to calculate a similarity matrix, rather than the co-occurrence matrix, between the different soil siblings. 
To do so, the map unit data from the soil survey (similar to the example showed Table \ref{tab:sim_mat_1}) was reshaped into a pseudo-community matrix (Table \ref{tab:sim_mat_3}), which uses the relative percentage of soil siblings to weight the presence of these siblings across map units. 
The resulting pseudo-community matrix was then standardised relative to the maximum relative presence for each soil sibling. 
The standardised matrix is then used to compute a distance matrix, based on the Jaccard distance [@legendre2012numerical]: 

\begin{equation}
D = 2 \times B / (1 + B)
\label{eq:jaccard}
\end{equation}
where $B(j,  k)$ is Bray-Curtis dissimilarity, defined as:
\begin{equation}
B(j, k) = \frac{\sum abs(X(i,j) - X(i, k))}{\sum (X(i, j) + X(i, k))}
\label{eq:bray}
\end{equation}
where X(i, j) and X(i, k) are the standardised quantity of soil siblings i and map units j and k. 
Finally, the similarity matrix (Table \ref{tab:sim_mat_4}) is obtained by [@kaufman2009finding]:

\begin{equation}
S = max(D) - D
\label{eq:similarity}
\end{equation}
where D is the distance matrix obtained via Equation \ref{eq:jaccard}, and S is the resulting similarity matrix.

Alternative methods to constructing a similarity matrix are also possible, such as the methods of revealed comparative advantage and cosine similarity as used by @Balassa:1965ta;@Hidalgo:2009p292 in economics, or the Brainerd-Robinson similarity used in archaeology [@Robinson:1951wy;@Giomi:2019fu]. 
Fundamentally, all these approaches seek to calculate pair-wise similarities between vectors of relative abundances, and the differences between them are essentially cosmetic [@Mills:2013hn]. 

\begin{table}
\begin{tabular}{ccccccccc}
\hline
 & 461845 & 461980 & 462528 & 462529 & 462530 & 462531 & 462954 & 462955 \\
\hline
Amador & 45 & 25 & 85 & 85 & 85 & 85 & 85 & 85 \\
Corning & 0 & 5 & 0 & 0 & 0 & 0 & 0 & 0\\
Exchequer & 0 & 0 & 5 & 5 & 5 & 5 & 0 & 0\\
Gillender & 40 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Hornitos & 0 & 0 & 5 & 5 & 5 & 5 & 10 & 10 \\
Inks & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Miltonhills & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Pardee & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Pentz & 0 & 0 & 5 & 5 & 5 & 5 & 5 & 5 \\
Peters & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Ranchoseco & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Redding & 0 & 4 & 0 & 0 & 0 & 0 & 0 & 0 \\
Vleck & 3 & 40 & 0 & 0 & 0 & 0 & 0 & 0\\
\hline
\end{tabular}
\caption{Pseudo-community matrix derived from the soil survey data. Each row represents a soil series, while each column represent a map unit code. The tranformation used the relative percentage of soil siblings to weight the presence of soil siblings across the different map units.}
\label{tab:sim_mat_3}
\end{table}

\begin{table}
\begin{tabular}{cccccccc}
\hline
& Gillender & Miltonhills & Pardee & Peters & Ranchoseco & Redding & Vleck \\
\hline
Amador & 0.5 & 0.03 & 0.07 & 0.03 & 0.03 & 0.01 & 0.03 \\
Gillender & 0 & 0.07 & 0.13 & 0.07 & 0.07 & 0.03 & 0.07 \\
Miltonhills & 0 & 0 & 0.50 & 0 & 0 & 0.40 & 0 \\        
Pardee & 0 & 0 & 0 & 0.50 & 0.50 & 0.20 & 0.50 \\
Peters & 0 & 0 & 0 & 0 & 1.00 & 0 & 1.00 \\
Ranchoseco & 0 & 0 & 0 & 0 & 0 & 0 & 1.00 \\
Redding & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
Vleck & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
\hline
\end{tabular}
\caption{Similarity matrix derived from the subset of soil suvey data presented in Table \ref{tab:sim_mat_1}}
\label{tab:sim_mat_4}
\end{table}

```{r ex_adj_mat, echo=FALSE, results='asis'}
# ex_m <- matrix(NA, ncol = 5, nrow = 5)
# rownames(ex_m) <- colnames(ex_m) <- LETTERS[1:5]
# ex_m[2, 1] <- 0.58
# ex_m[3, 1] <- ex_m[3, 2] <- ex_m[4, 3] <- ex_m[5, 1] <- ex_m[5, 2] <- ex_m[5, 4] <- 0.00
# ex_m[4, 1] <- 0.34
# ex_m[4, 2] <- 0.12
# ex_m[5, 3] <- 0.27
# ex_m[2, 1] <- 0.58
# ex_m[3, 1] <- ex_m[3, 2] <- ex_m[4, 3] <- ex_m[5, 1] <- ex_m[5, 2] <- ex_m[5, 4] <- 0.00
# ex_m[4, 1] <- 0.34
# ex_m[4, 2] <- 0.12
# ex_m[5, 3] <- 0.27

# ex_m <- matrix(NA, ncol = 8, nrow = 8)
# colnames(ex_m) <- c('Amador', 'Gillender', 'Miltonhills', 'Pardee', "Peters", 'Ranchoseco', 'Redding', 'Vleck')
# rownames(ex_m) <- c('Amador', 'Gillender', 'Miltonhills', 'Pardee', "Peters", 'Ranchoseco', 'Redding', 'Vleck')
# ex_m[1,] <- c(1.00, 0.5, 0.03, 0.07, 0.03, 0.03, 0.01, 0.03)
# ex_m[2,] <- c(0.5, 1.00, 0.07, 0.13, 0.07, 0.07, 0.03, 0.07)
# ex_m[3,] <- c(0, 0, 1.00,  0.50, 0, 0, 0.40, 0)
# ex_m[4,] <- c(0, 0, 0, 1.00, 0.50, 0.50, 0.20, 0.50)
# ex_m[5,] <- c(0, 0, 0, 0, 1.00, 0, 0, 1.00)
# ex_m[6,] <- c(0, 0, 0, 0, 0, 1.00, 0, 1.00)
# ex_m[7,] <- c(0, 0, 0, 0, 0, 0, 1.00, 0)
# ex_m[8,] <- c(0, 0, 0, 0, 0, 0, 0, 1.00)
# ex_m[lower.tri(ex_m)] <- ex_m[upper.tri(ex_m)]

data(amador, package = "sharpshootR")
ex_m <- sharpshootR::component.adj.matrix(amador)

# d <- data.frame(ex_m)
# diag(d) <- rep('-', times = 5)
# d[is.na(d)] <- ''
# 
# knitr::kable(d, caption = "Example adjacency matrix")
```

<!-- This method was implemented in the R package `sharpshootR` [REFERENCE]. -->

### Graph representation of the soil series associations

In this study, we used the similarity matrix S calculated from the soil survey data matrix using Equation \ref{eq:similarity} as an adjacency matrix to represent the associations of different soil series within the map units. 
The matrix S was then used to generate an undirected graph representation of the associations between soil siblings (Figure \ref{fig:ex_graph}). 
In this case, nodes of the graph represent the different soil series, and the edges indicate the pair-wise co-occurrence of the soil series within map units. 
Weights on the edges can also be used to indicate the strength of the co-occurrence likelihood. 
The Fruchterman-Reingold layout [@fruchterman1991graph] was used to project the undirected graph as a data visualisation. 
This is a so-called force-spring layout which treats the nodes in the graph as repelling particles, connected via springs (the edges) which constrain them from moving apart. the resulting layout is non-unique but nodes (series) that are more strongly connected via co-occurences will be spatial clustered, while those that are dissimilar will be further apart. 

```{r ex_graph, echo=FALSE, fig.height=6, fig.width=8, fig.cap="\\label{fig:ex_graph}Generation of an undirected graph representation of soils urvey data. (a) Soil series represented as vertices. (b) "}
ex_g <- graph.adjacency(ex_m, mode = "upper", weighted = TRUE)

# Size (abundance)
# V(ex_g)$size <- c(6, 4, 3.5, 3, 3, 2, 1, 1)
# E(ex_g)$weight[is.na(E(ex_g)$weight)] <- 0
weight <- E(ex_g)$weight
vertexSize <- degree(ex_g)
V(ex_g)$size <- sqrt(vertexSize/max(vertexSize)) * 10 * 2

# Colours (community membership)
g.com <- igraph::cluster_fast_greedy(ex_g)
g.com.membership <- igraph::membership(g.com)
cols <- RColorBrewer::brewer.pal(n = length(g.com), name = 'Set3')
V(ex_g)$color <- cols[g.com.membership]

# plot.igraph(ex_g, edge.width = 10 * E(ex_g)$weight, layout = layout.fruchterman.reingold)

p_ex_graph <- ggraph(ex_g, layout = "igraph", algorithm = "fr", niter = 5000)

p_ex_graph_0 <- p_ex_graph + 
  geom_node_point(size = 10, fill = "grey70", colour = "grey10", show.legend = FALSE, shape = 21) +
  geom_node_text(aes(label = name), repel = FALSE) +
  scale_size(range = c(6, 20)) +
  # Expand to make room for larger node sizes
  scale_x_continuous(expand = expand_scale(add = 1)) + 
  scale_y_continuous(expand = expand_scale(add = 1)) +
  #lims(x = c(64, 67), y = c(63, 66.5)) +
  theme_graph()

p_ex_graph_1 <- p_ex_graph + 
  geom_edge_link(colour = "grey50") +
  geom_node_point(size = 10, fill = "grey70", colour = "grey10", show.legend = FALSE, shape = 21) +
  geom_node_text(aes(label = name), repel = FALSE) +
  scale_size(range = c(6, 20)) +
  # Expand to make room for larger node sizes
  scale_x_continuous(expand = expand_scale(add = 1)) + 
  scale_y_continuous(expand = expand_scale(add = 1)) +
  #lims(x = c(64, 67), y = c(63, 66.5)) +
  theme_graph()

p_ex_graph_2 <- p_ex_graph + 
  geom_edge_link(aes(edge_width = weight), colour = "grey50", show.legend = FALSE) +
  geom_node_point(aes(size = size), fill = "grey70", colour = "grey10", show.legend = FALSE, shape = 21) +
  geom_node_text(aes(label = name), repel = FALSE) +
  scale_size(range = c(6, 20)) +
  scale_edge_width_continuous(range = c(1, 3)) +
  # Expand to make room for larger node sizes
  scale_x_continuous(expand = expand_scale(add = 1)) + 
  scale_y_continuous(expand = expand_scale(add = 1)) +
  #lims(x = c(64, 67), y = c(63, 66.5)) +
  theme_graph()

p_ex_graph_3 <- p_ex_graph + 
  geom_edge_link(aes(edge_width = weight), colour = "grey50", show.legend = FALSE) +
  geom_node_point(aes(size = size, fill = color), colour = "grey10", show.legend = FALSE, shape = 21) +
  # geom_node_text(aes(label = name), colour = "white", size = 4, repel = FALSE) +
  geom_node_text(aes(label = name), repel = FALSE) +
  scale_size(range = c(6, 20)) +
  scale_edge_width_continuous(range = c(1, 3)) +
  # Expand to make room for larger node sizes
  scale_x_continuous(expand = expand_scale(add = 1)) + 
  scale_y_continuous(expand = expand_scale(add = 1)) +
  #lims(x = c(64, 67), y = c(63, 66.5)) +
  theme_graph()

# cowplot::plot_grid(
#   p_ex_graph_0, p_ex_graph_1, p_ex_graph_2, p_ex_graph_3, 
#   nrow = 2, 
#   labels = "auto",
#   align = "h", label_x = 0.5, label_y = 0
#   )

p_ex_graph_0 + p_ex_graph_1 + p_ex_graph_2 + p_ex_graph_3 + plot_layout(ncol = 2) 
```

## Soil survey graph analysis

### Soil series communities identification

A community structure detection method was applied on the undirected graph derived from the soil survey data. 
Community detection on networks seeks to identify clusters of nodes that are more strongly connected within the cluster than they are to nodes in other clusters. 
The most common method of algorithmically identifying communities is modularity optimisation. 
This determines a set of non-overlapping partitions of the nodes in the network. 
Unlike other clustering methods such as k-means, the optimal number of clusters or communities is determined as part of the community detection.  
Here we used the fast greedy modularity optimisation algorithm [@clauset2004finding].  

### Network metrics

A range of network metrics can be derived from the topology of the graph. Below, we list some metrics that are of potential use for investigating/understanding soil networks. These can be split into local measures (specific to each node) and global measures (that apply to the whole network).

- **Number of connected components:** Networks do not need to comprise of a single connected component.  The number of connected components of a network is the number of distinct subgraphs that the network is comprised of. For example it is possible to have an isolated pair of soil series that are connected to each other, but to no other series in the network.
- **Number of communities:** This is derived from the community detection results. Since communities can not span across disconnected subgraphs, the number of communities is bounded below by the number of connected components.
 - **Node Centrality:** This measures, broadly, the ``importance'' of a node in the topology of the network. A number of different centrality measures exist. We consider the following:
    - Node degree: this simply the number of links or edges connected to a node. It gives an indication of how "ubiquitous"/"social" a soil series -- ie high degree centrality, that's a soil series that co-occur with many others.
    - Node strength: for weighted networks, the strength of a node is the sum of the weights of the edges connected to that node. For unweighed netowrks, node strength is equal to degree centrality.
    - PageRank: A popular variant of eigenvector centrality. Eigenvector-based measures consider not only the strength of a node but also how well connected a node is to other nodes with high node strength. That is, if the soil series that a node is connected to is also highly connected. (Socialbale soils connected to other sociable soils.)
    - Betweeness centrality:  The number of weighted shortest paths that pass through a node, given all possible paths between pairs of nodes in the network. In the context of soil networks, series with high betweenness centrality are those that are found in common with multiple communities of soil series. that is they share similarity with soils from more than one community of soils
 
 FOR DISCUSSION Suggest they can adapt to different soil forming factors combination? Reveal soil that have ubiquitous soil formation processes? 

--> Try and plot spatial map based on centrality
--> The issue with betweeness is that it does not distinguish between "bridginess" between community vs. being in the middle of heaps of links. To analyse the "bridgy" soil series, we might pick them manually from the network.  

```{r metrics, echo=FALSE}
# Node degree
V(g)$degree <- degree(g)
# Node strength
V(g)$strength <- strength(g)
# PageRank
V(g)$pr <- page_rank(g)$vector
# Betweeness
V(g)$betweeness <- betweenness(g)

# Bridge centrality
# see https://rdrr.io/cran/networktools/man/bridge.html
br <- networktools::bridge(g, communities = V(g)$cluster)

V(g)$br_strength <- br$`Bridge Strength`
V(g)$br_btw <- br$`Bridge Betweenness`
V(g)$br_close <- br$`Bridge Closeness`
V(g)$br_inf1 <- br$`Bridge Expected Influence (1-step)`
V(g)$br_inf2 <- br$`Bridge Expected Influence (2-step)`
```

## Implementation

The methods described in this paper have been implemented in the R statistical environment [REFERENCE] as part of the `aqp` and `sharpshootR` packages [@beaudette2013algorithms].
The graph was created in R based on the `graph.adjacency` method available in the `igraph` package [REFERENCE]. `cluster_fast_greedy`

Results
=======

## Components per map unit

The number of soil series identified by the pedologist as a component is varying over the surveyed area. 
Figure \ref{fig:components_per_polygon} shows the distribution of the number of soil components in every map unit that have been recorded in the region. 
Results show that a large majority of map units are mapped using more than one soil component, with the average number of components used being around 3. 
This shows that most map units record a co-occurence between three or more soil siblings. 

```{r components_per_polygon, echo=FALSE, fig.cap="\\label{fig:components_per_polygon}Number of soil components mapped in the different map units in the surveyed region.", fig.width=6, fig.height=4}
# Number of components per polygon
p_comp_per_pols <- x %>% 
  # dplyr::group_by(dmudesc) %>%
  dplyr::group_by(mukey) %>%
  dplyr::summarise(
    n_per_mu = n()
  ) %>%
  group_by(n_per_mu) %>% 
  dplyr::summarise(n = n()) %>% 
  ggplot() + 
    geom_bar(aes(x = n_per_mu, y = n), stat = "identity") + 
    labs(x = "Number of components per map unit", y = "Count") +
    scale_x_continuous(breaks = 1:8) +
    theme_bw()

print(p_comp_per_pols)
```

## Abundance

```{r fig_abundance, echo=FALSE, fig.cap="\\label{fig:abundance}Relative abundance of the different soil components found in the surveyed region."}
p_ab <- abundance %>% 
  # dplyr::filter(as.numeric(abundance_ha) > 5) %>% 
  ggplot() +
  geom_bar(aes(y = as.numeric(abundance_ha), x = reorder(compname, -abundance_ha)), stat = "identity") +
  labs(y = "Area (ha)", x = "Soil series") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(p_ab)
```

## Adjacency graph 

<!-- ```{r adjacency_mat, echo=FALSE, cache=TRUE, fig.cap="\\label{fig:adjacency_mat}Co-occurence probability matrix"} -->
<!-- # adjacency matrix -->
<!-- p_adj_mat <- reshape2::melt(m) %>%  -->
<!--   ggplot() +  -->
<!--     geom_tile(aes(x = Var1, y = Var2, fill = value), colour = "grey90", size = 0.05) +  -->
<!--     theme_bw() +  -->
<!--     theme(axis.text = element_blank(), axis.ticks = element_blank()) + -->
<!--     # scale_fill_continuous(low = "white", high = "red", guide = guide_legend(title = "")) +  -->
<!--     scale_fill_gradientn( -->
<!--       colours = c("#ffffff", RColorBrewer::brewer.pal(n = 5, name = "Reds")), -->
<!--       guide = guide_legend(title = "") -->
<!--     ) + -->
<!--     labs(x = "", y = "") + -->
<!--     # ggtitle("Co-occurence probability matrix") + -->
<!--     coord_equal() -->

<!-- print(p_adj_mat) -->
<!-- ``` -->

```{r process_graphs, echo=FALSE, message=FALSE, cache=TRUE}
k <- igraph_to_networkD3(g, group = V(g)$cluster)

vertex_df <- data.frame(
  name = V(g)$name,
  color = V(g)$color,
  size = V(g)$size,
  notes = V(g)$notes
)

k$nodes <- data.frame(k$nodes, vertex_df)
k$links <- data.frame(k$links, weight = E(g)$weight)

colour_scale_data <- k$nodes %>% 
  dplyr::group_by(group) %>% 
  dplyr::summarise(
    color = unique(color),
    notes = unique(notes)
  ) %>% 
  dplyr::mutate(
    cl = as.character(group), 
    color_simple = stringr::str_sub(color, start = 1, end = 7)
  )
```

```{r draw_graphs, echo=FALSE, message=FALSE, cache=TRUE}
p_g0 <- ggraph(g, layout = "fr", niter = 50000) +
  geom_edge_link(colour = "grey70") +
  geom_node_point(alpha = 0.9) +
  coord_equal() +
  ggraph::theme_graph(base_family = "sans")

p_g1 <- p_g0 + 
  geom_node_point(aes(size = size), alpha = 0.9) +
  scale_size(guide = FALSE)

p_g2 <- p_g1 +
  geom_node_point(aes(size = size, color = as.factor(cluster)), alpha = 0.9) +
  scale_colour_manual(values = colour_scale_data$color_simple, guide = FALSE) +
  scale_size(guide = FALSE)

p_g3 <- p_g2 +
  geom_node_text(aes(label = name), repel = TRUE) 

p_g4 <- p_g2 +
  scale_colour_manual(values = colour_scale_data$color_simple, labels = colour_scale_data$notes, guide = guide_legend(title = ""))

p_g5 <- p_g2 +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_manual(values = colour_scale_data$color_simple, labels = colour_scale_data$notes, guide = guide_legend(title = ""))
```

The existence of co-occuring soil series across the surveyed region allowed for the computation of a similarity matrix, as presented in the Methods section. 
This similarity matrix was then used to build the adjacency graph of the soil survey, which is shown Figure \ref{fig:plot_graph_annotated}. 
The resulting visualisation shows a main network, surrounded by 8 other, much smaller networks. 
This shows that... 

Figure \ref{fig:plot_graph_annotated} shows the communities identified from the graph structure, and how these cluster the different soil series present in the soil survey area.  
Ultimately, 16 different communities were delineated by the algorithm. 

```{r plot_graph_annotated, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="\\label{fig:plot_graph_annotated}Correspondance between identified communities from the graph structure and soil series.", fig.width=6, fig.height=8}
# cowplot::plot_grid(p_g1, p_g2, p_g3, nrow = 1, labels = "auto", align = "h", label_x = 0.5, label_y = 0)
p_g5 + theme(legend.position = "none")
```

## Graph metrics

```{r plot_metrics, echo=FALSE, message=FALSE, warning=FALSE}
# Node degree
p_degree <- p_g1 +
  geom_node_point(aes(size = size, color = degree), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Node degree")
  )

# Node strength
p_strength <- p_g1 +
  geom_node_point(aes(size = size, color = strength), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Node strength")
  )

# PageRank
p_pr <- p_g1 +
  geom_node_point(aes(size = size, color = pr), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "PageRank")
  )

# Betweeness
p_betweeness <- p_g1 +
  geom_node_point(aes(size = size, color = betweeness), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Betweeness")
  )

p_degree + p_strength + p_pr + p_betweeness + plot_layout(ncol = 2)
```

```{r plot_metrics_2, echo=FALSE, message=FALSE, warning=FALSE}
# V(g)$br_strength <- br$`Bridge Strength`
# V(g)$br_btw <- br$`Bridge Betweenness`
# V(g)$br_close <- br$`Bridge Closeness`
# V(g)$br_inf1 <- br$`Bridge Expected Influence (1-step)`
# V(g)$br_inf2 <- br$`Bridge Expected Influence (2-step)`
p_br_strength <- p_g1 +
  geom_node_point(aes(size = size, color = betweeness), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Bridge Strength")
  )

p_br_btw <- p_g1 +
  geom_node_point(aes(size = size, color = br_btw), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Bridge Betweenness")
  )

p_br_close <- p_g1 +
  geom_node_point(aes(size = size, color = br_close), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Bridge Closeness")
  )

p_br_inf1 <- p_g1 +
  geom_node_point(aes(size = size, color = br_inf1), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Bridge Expected Influence (1-step)")
  )

p_br_inf2 <- p_g1 +
  geom_node_point(aes(size = size, color = br_inf2), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_colour_viridis_c(
    option = "magma",
    guide = guide_legend(title = "Bridge Expected Influence (2-step)")
  )

p_br_btw + p_br_btw + p_br_close + p_br_inf1 + p_br_inf2 + plot_layout(ncol = 2)
```

# Discussion

## Expert interpretation of the detected communities

```{r plot_graph_4, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="\\label{fig:plot_graph_4}Expert interpretation of the communities.", fig.width=6, fig.height=8}
p_g5 + theme(legend.position = "bottom")
```

<!-- ```{r map_communities, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="\\label{fig:map_communities}Map of the communities identified on the graph.", fig.width=10, fig.height=8} -->
<!-- p <- mu_union %>% #left_join(colour_scale_data, by = c()) %>%  -->
<!--   ggplot() +  -->
<!--   geom_sf(aes(fill = notes), colour = "grey70", lwd = 0.05) +  -->
<!--   scale_fill_manual(values = colour_scale_data$color_simple, labels = mu_union$cl, guide = guide_legend(title = "")) + -->
<!--   # scale_fill_manual(values = mu_union$color, guide = guide_legend(title = "")) +  -->
<!--   theme_bw() -->

<!-- print(p) -->
<!-- ``` -->

```{r map_entropy, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="\\label{fig:map_entropy}Shannon's entropy values for each map unit.", fig.width=10, fig.height=8}
map_entropy <- st_read('../data/mu-with-cluster-membership.gpkg', quiet = TRUE) %>%
  ggplot() + 
  geom_sf(aes(fill = H), colour = NA) + 
  scale_fill_viridis("Shannon's entropy") + 
  theme_bw()

print(map_entropy)
```

```{r map_communities_interp, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="\\label{fig:map_communities_interp}Map of the communities identifies on the graph, along with their expert interpretation. The colours used for the detected communities are the same as the one used Figure \\ref{plot_graph_4}.", fig.width=10, fig.height=8}
## TODO: I need to include the cluster narrative when making the mu_sf source data

# mu_notes <- mu_sf %>% 
#   dplyr::select(-notes) %>% # remove redundant columns
#   dplyr::mutate(cluster = as.character(cluster)) %>% 
#   dplyr::left_join(
#     dplyr::mutate(colour_scale_data, cluster = as.character(group)), 
#     by = "cluster"
#   )

mu.simple.sf <- st_read('../data/graph-and-mu-polygons.gpkg', quiet = TRUE)

pn <- mu.simple.sf %>% #mutate(id = as.numeric(cl)) %>% arrange(id) %>% 
  ggplot() + 
  geom_sf(aes(fill = as.factor(cluster)), colour = "grey30", lwd = 0.1) + 
  scale_fill_manual(
    values = leg$color, 
    labels = leg$notes,
    guide = guide_legend(title = "")
  ) +
  # scale_fill_manual(values = mu_union$color, guide = guide_legend(title = "")) + 
  theme_bw()

print(pn)

# Facetted map in case we want to switch to that
pn_fac <- mu.simple.sf %>% 
  left_join(leg) %>% 
  ggplot() + 
    geom_sf(data = dplyr::select(mu.simple.sf, -cluster), fill = "gray80", colour = "gray30", lwd = 0.05) +
    geom_sf(aes(fill = as.factor(cluster)), colour = "grey30", lwd = 0.1) + 
    scale_fill_manual(
        values = leg$color, 
        labels = leg$notes,
        guide = guide_legend(title = "")
    ) +
    theme_bw() + 
  facet_wrap(~cluster)

```

## Relationship to various soil-forming factors

The objective validation of the soilscapes delineated by community detection of the adjacency graph is a difficult task. 
In this study we have decided to look at the distribution of a range of soil-forming factors across the different soilscapes.

## Limitations

- we do not deal with spatial co-occurence
- level of taxonomy this is run can be discussed, but we feel soil serie is a right choice
- more to it than the map



# Conclusion

References {#references .unnumbered}
==========
